resevol: an R package for spatially explicit models of pesticide resistance

### 2022-11-19 notebook/ms/advanced_techniques.Rmd
Here I'm committing some change that appears to have been made to the advanced techniques, I believe to the author details

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
subtitle: Advanced techniques (Supporting Information 2)
author: |
  | A. Bradley Duthie&#xb9;&#xb2;, et al.
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  word_document:
    reference_docx: docx_template.docx
  pdf_document:
    toc: no
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---

>>>>

---
title: 'resevol: an R package for spatially explicit models of pesticide resistance
  given evolving pest genomes'
subtitle: Advanced techniques (Supporting Information 2)
author: |
  | A. Bradley Duthie&#xb9; &#179;, Rosie Mangan&#xb9;, Chintamani Rose McKeon&#xb9;,
  | Matthew C. Tinsley&#xb9;, and Luc F. Bussi&egrave;re&#xb2;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2]  alexander.duthie@stir.ac.uk, Biological and Environmental Sciences 3A149
  University of Stirling Stirling, FK9 4LA, UK'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    toc: no
  word_document:
    reference_docx: docx_template.docx
  pdf_document:
    toc: no
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{RESEVOL, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: resevol.bib
biblio-style: apalike
---
